ext_risk_copula

### 2019-02-17 ext_risk_copula.Rmd
running code with acf on 26 timesteps and omitting austin-brewer results

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

@@

# Austin Brewer model :

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

@@

>>>>

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

<!--
# Austin Brewer model :

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }
-->
